---
title: "HW1"
output: html_document
---

# Question 1

Supervised learning: consists of a target / outcome variable which is to be predicted from a given set of predictors;generates a function that map inputs to desired outputs, and training process continues until the model achieves a desired level of accuracy on the training data

Unsupervised learning:assumes that the input dataset is distributed according to some unknown underlying statistical distribution; attempts to find clusters or groups in the data without any labels for what constitutes a "cluster" or "group"

Main difference:supervised learning uses labeled input and output data, while unsupervised does not

# Question 2

# Question 3

# Question 4

# Question 5

# Question 6

# Exercise 1

```{r}
library(tidyverse)
hist(mpg$hwy,main = "Highway Miles Per Gallon",xlab = "Hwy Miles")
```
In the histogram, we can see there is a bi-modal distribution that is slightly right-skewed. The center is also around 23, while the spread is from 10 to 45, with a range about 35. 

# Exercise 2
```{r}
library(ggplot2)
ggplot(mpg, aes(hwy,cty)) + geom_point()
```
Yes, there seems to be a relationship between hwy and cty as a positive correlation appears in the scatterplot. This indicates that when the highway mileage increases, so does the city mileage.

# Exercise 3
```{r}
ggplot(mpg, aes(y = manufacturer)) +
geom_bar()


```


# Exercise 4

# Exercise 5

# Exercise 6